Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-12-22 threshold/draft.Rnw
Clarified discussion of pruning efficiency, indicating t=0.99

Pairs of vectors below the correlation threshold that lie more than one index
difference apart relative to the permutation $P$ can be similarly pruned by
replacing $D^1$ with $D^j$, $j=2,3,\ldots,\ell$ in the above expressions.
Following this process, we can produce a well-pruned candidate set of vector
pairs that contains all pairs that meet a given correlation threshold using
$\ell$ matrix vector products with matrices of order $n \times p$, where $p$ is
chosen in practice such that $p<<k$. Setting $p=10$ for the example shown in
Figure \ref{fig1} prunes all but $12,924$ possible vector pairs out of a total
$6221(6221 - 1) = 193,47,310$ with $\ell=1,715$.

>>>>

Pairs of vectors below the correlation threshold that lie more than one index
difference apart relative to the permutation $P$ can be similarly pruned by
replacing $D^1$ with $D^j$, $j=2,3,\ldots,\ell$ in the above expressions.
Following this process, we can produce a well-pruned candidate set of vector
pairs that contains all pairs that meet a given correlation threshold using
$\ell$ matrix vector products with matrices of order $n \times p$, where $p$ is
chosen in practice such that $p<<k$. Setting $p=10$ for the example shown in
Figure \ref{fig1} with $t=0.99$ prunes all but $149$ possible vector pairs out of a total
$6221(6221 - 1) = 193,47,310$ with $\ell=787$.
